Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-08-02 Document/paper.tex
edit

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}
\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}
\end{center}
\caption{\textbf{RP: Maybe add DMO and MHD directly to the two panels?} Axial ratios for all simulated halos.
  Left/right panel corresponds to DMO/MHD simulations, respectively.
  Triangles (squares) represent the measurements at $R_{200}/16$
  ($R_{200}$) that correspond to physical distances of $14\pm 1$ kpc
  ($230\pm 15$ kpc).
  Here we visualize three main population trends.
  First, in DMO simulations halos are rounder in the outskirts
  than in the inner part.
  Second, halos in MHD are rounder than its DMO counterparts.
  Third, halos in MHD are rounder in the inner regions than in
  the outskirts (opposite to the DMO trend). \textbf{RP: is that last point really statistically the case? The average points that were in the plot before seemed to be consistent within scatter for the MHD run} }
  \label{fig:triaxiality_plane}
\end{figure*}

@@

We summarize this trend in Figure \ref{fig:triaxiality_plane} by
plotting the results of all the 30 halos in the DMO sample.
The left panel shows every halo in the $c/a$-$b/a$ plane at
two different radii $R_{200}/8 (\sim 20$kpc$)$ \textbf{RP: the plots says R200/16} and $R_{200}$. 
The outer part of the halo is systematically rounder than its inner
region. 
Nevertheless the halo shape can still be considerated to be prolate at
all radii.

@@

We now quantify this change in triaxility at the level of individual halos.
We compute $\Delta T\equiv T_{\rm MHD}-T_{\rm DMO}$ to quantify the
change between the triaxility in the MHD and the DMO simulation.
Figure \ref{fig:delta_triaxial_cumulative} shows the cumulative
distribution at the same radii as in
Figure \ref{fig:delta_triaxial_cumulative}.  
From this Figure we observe that at $R_{200}$ all the halos have
reduced its triaxility include baryonic physics.
At smaller radii this general trend continues, although there is a
small fraction ($\approx 1/15$) \textbf{RP: just write 2 in out sample?} of halos that slightly increased their
triaxility with MHD physics. 
However, this small fraction correspond to halos that already were
outliers in the DMO sample and had triaxilities around $1/3$,
considerably lower than its parent sample.

@@

\begin{table*}
  \centering 
  \begin{tabular}{r r r r r r r r r r r}
  \hline\hline
  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
  \hline
Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
Au-2 & 0.93 & 0.61 & 0.95 & 0.58 & 0.96 & 0.61 & 0.96 & 0.65 & 0.88 & 0.65\\
Au-3 & 0.97 & 0.66 & 0.96 & 0.66 & 0.94 & 0.70 & 0.93 & 0.76 & 0.94 & 0.79\\
Au-4 & 0.88 & 0.77 & 0.82 & 0.79 & 0.80 & 0.76 & 0.85 & 0.79 & 0.83 & 0.76\\
Au-5 & 0.97 & 0.79 & 0.94 & 0.80 & 0.92 & 0.81 & 0.94 & 0.82 & 0.94 & 0.81\\
Au-6 & 0.98 & 0.60 & 0.96 & 0.60 & 0.92 & 0.63 & 0.86 & 0.63 & 0.78 & 0.61\\
Au-7 & 0.95 & 0.66 & 0.95 & 0.66 & 0.97 & 0.68 & 0.97 & 0.69 & 0.96 & 0.70\\
Au-8 & 0.99 & 0.59 & 0.97 & 0.62 & 0.92 & 0.66 & 0.76 & 0.57 & 0.83 & 0.58\\
Au-9 & 0.94 & 0.75 & 0.93 & 0.73 & 0.92 & 0.73 & 0.93 & 0.79 & 0.92 & 0.82\\
Au-10 & 0.95 & 0.85 & 0.94 & 0.85 & 0.93 & 0.85 & 0.92 & 0.82 & 0.91 & 0.80\\
Au-11 & 0.54 & 0.49 & 0.55 & 0.48 & 0.61 & 0.53 & 0.60 & 0.53 & 0.62 & 0.57\\
Au-12 & 0.95 & 0.77 & 0.88 & 0.81 & 0.90 & 0.84 & 0.92 & 0.81 & 0.95 & 0.82\\
Au-13 & 0.95 & 0.88 & 0.96 & 0.88 & 0.98 & 0.82 & 0.94 & 0.76 & 0.82 & 0.62\\
Au-14 & 0.95 & 0.75 & 0.93 & 0.79 & 0.91 & 0.80 & 0.91 & 0.79 & 0.93 & 0.81\\
Au-15 & 0.99 & 0.67 & 0.98 & 0.75 & 0.94 & 0.79 & 0.93 & 0.81 & 0.88 & 0.76\\
Au-16 & 0.99 & 0.69 & 0.99 & 0.70 & 0.99 & 0.74 & 0.98 & 0.76 & 0.99 & 0.99\\
Au-17 & 0.96 & 0.79 & 0.96 & 0.80 & 0.97 & 0.82 & 0.96 & 0.83 & 0.96 & 0.87\\
Au-18 & 0.93 & 0.76 & 0.92 & 0.74 & 0.86 & 0.72 & 0.81 & 0.71 & 0.74 & 0.66\\
Au-19 & 0.95 & 0.67 & 0.91 & 0.63 & 0.89 & 0.63 & 0.83 & 0.64 & 0.85 & 0.69\\
Au-20 & 0.81 & 0.58 & 0.91 & 0.64 & 0.95 & 0.71 & 0.97 & 0.78 & 0.86 & 0.77\\
Au-21 & 0.98 & 0.74 & 0.97 & 0.82 & 0.97 & 0.87 & 0.99 & 0.88 & 0.99 & 0.99\\
Au-22 & 0.96 & 0.84 & 0.93 & 0.84 & 0.93 & 0.85 & 0.95 & 0.87 & 0.97 & 0.88\\
Au-23 & 0.94 & 0.65 & 0.96 & 0.64 & 0.94 & 0.65 & 0.92 & 0.69 & 0.93 & 0.74\\
Au-24 & 0.99 & 0.67 & 1.00 & 0.63 & 0.99 & 0.65 & 0.97 & 0.68 & 0.98 & 0.70\\
Au-25 & 0.97 & 0.71 & 0.96 & 0.73 & 0.86 & 0.74 & 0.67 & 0.64 & 0.71 & 0.67\\
Au-26 & 0.96 & 0.76 & 0.97 & 0.73 & 0.97 & 0.70 & 0.99 & 0.68 & 0.97 & 0.67\\
Au-27 & 0.98 & 0.73 & 0.97 & 0.75 & 0.97 & 0.79 & 0.96 & 0.79 & 0.95 & 0.77\\
Au-28 & 0.98 & 0.82 & 0.94 & 0.77 & 0.88 & 0.73 & 0.86 & 0.74 & 0.93 & 0.75\\
Au-29 & 0.91 & 0.81 & 0.89 & 0.72 & 0.87 & 0.69 & 0.84 & 0.68 & 0.85 & 0.69\\
Au-30 & 0.89 & 0.73 & 0.78 & 0.64 & 0.69 & 0.53 & 0.80 & 0.58 & 0.91 & 0.63\\
  \hline\hline
  \end{tabular}
  \label{tab}
  \caption{Magnetic field properties of the Auriga galaxies at $z=0$. For general properties of the disks.}
\end{table*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}
\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}
\end{center}
\caption{Axial ratios for all simulated halos.
  Left/right panel corresponds to DMO/MHD simulations, respectively.
  Triangles (squares) represent the measurements at $R_{200}/16$
  ($R_{200}$) that correspond to physical distances of $14\pm 1$ kpc
  ($230\pm 15$ kpc).
  Here we visualize three main population trends.
  First, in DMO simulations halos are rounder in the outskirts
  than in the inner part.
  Second, halos in MHD are rounder than its DMO counterparts.
  Third, halos in MHD are rounder in the inner regions than in
  the outskirts (opposite to the DMO trend). \textbf{RP: is that last point really statistically the case? The average points that were in the plot before seemed to be consistent within scatter for the MHD run} }
  \label{fig:triaxiality_plane}
\end{figure*}

@@

We summarize this trend in Figure \ref{fig:triaxiality_plane} by
plotting the results of all the 30 halos in the DMO sample.
The left panel shows every halo in the $c/a$-$b/a$ plane at
two different radii $R_{200}/16 (\sim 20$kpc$)$ and $R_{200}$. 
The outer part of the halo is systematically rounder than its inner
region. 
Nevertheless the halo shape can still be considerated to be prolate at
all radii.

@@

We now quantify this change in triaxility at the level of individual halos.
We compute $\Delta T\equiv T_{\rm MHD}-T_{\rm DMO}$ to quantify the
change between the triaxility in the MHD and the DMO simulation.
Figure \ref{fig:delta_triaxial_cumulative} shows the cumulative
distribution at the same radii as in
Figure \ref{fig:delta_triaxial_cumulative}.  
From this Figure we observe that at $R_{200}$ all the halos have
reduced its triaxility include baryonic physics.
At smaller radii this general trend continues, although 2 haloes (Au-11 and Au-17) 
in our sample increased their triaxility with MHD physics. 
However, this small fraction correspond to halos that already were
outliers in the DMO sample and had triaxilities around $1/3$,
considerably lower than its parent sample.

@@

\begin{table*}
  \centering 
  \begin{tabular}{c c c c c c c c c c c}
  \hline\hline
  Halo & $(b/a)_{16}$ & $(c/a)_{16}$& $(b/a)_{8}$ & $(c/a)_{8}$& $(b/a)_{4}$ & $(c/a)_{4}$& $(b/a)_{2}$ & $(c/a)_{2}$& $(b/a)_{1}$ & $(c/a)_{1}$ \\
  \hline
Au-1 & 0.94 & 0.65 & 0.96 & 0.66 & 0.96 & 0.70 & 0.92 & 0.68 & 0.91 & 0.67\\
Au-2 & 0.93 & 0.61 & 0.95 & 0.58 & 0.96 & 0.61 & 0.96 & 0.65 & 0.88 & 0.65\\
Au-3 & 0.97 & 0.66 & 0.96 & 0.66 & 0.94 & 0.70 & 0.93 & 0.76 & 0.94 & 0.79\\
Au-4 & 0.88 & 0.77 & 0.82 & 0.79 & 0.80 & 0.76 & 0.85 & 0.79 & 0.83 & 0.76\\
Au-5 & 0.97 & 0.79 & 0.94 & 0.80 & 0.92 & 0.81 & 0.94 & 0.82 & 0.94 & 0.81\\
Au-6 & 0.98 & 0.60 & 0.96 & 0.60 & 0.92 & 0.63 & 0.86 & 0.63 & 0.78 & 0.61\\
Au-7 & 0.95 & 0.66 & 0.95 & 0.66 & 0.97 & 0.68 & 0.97 & 0.69 & 0.96 & 0.70\\
Au-8 & 0.99 & 0.59 & 0.97 & 0.62 & 0.92 & 0.66 & 0.76 & 0.57 & 0.83 & 0.58\\
Au-9 & 0.94 & 0.75 & 0.93 & 0.73 & 0.92 & 0.73 & 0.93 & 0.79 & 0.92 & 0.82\\
Au-10 & 0.95 & 0.85 & 0.94 & 0.85 & 0.93 & 0.85 & 0.92 & 0.82 & 0.91 & 0.80\\
Au-11 & 0.54 & 0.49 & 0.55 & 0.48 & 0.61 & 0.53 & 0.60 & 0.53 & 0.62 & 0.57\\
Au-12 & 0.95 & 0.77 & 0.88 & 0.81 & 0.90 & 0.84 & 0.92 & 0.81 & 0.95 & 0.82\\
Au-13 & 0.95 & 0.88 & 0.96 & 0.88 & 0.98 & 0.82 & 0.94 & 0.76 & 0.82 & 0.62\\
Au-14 & 0.95 & 0.75 & 0.93 & 0.79 & 0.91 & 0.80 & 0.91 & 0.79 & 0.93 & 0.81\\
Au-15 & 0.99 & 0.67 & 0.98 & 0.75 & 0.94 & 0.79 & 0.93 & 0.81 & 0.88 & 0.76\\
Au-16 & 0.99 & 0.69 & 0.99 & 0.70 & 0.99 & 0.74 & 0.98 & 0.76 & 0.99 & 0.99\\
Au-17 & 0.96 & 0.79 & 0.96 & 0.80 & 0.97 & 0.82 & 0.96 & 0.83 & 0.96 & 0.87\\
Au-18 & 0.93 & 0.76 & 0.92 & 0.74 & 0.86 & 0.72 & 0.81 & 0.71 & 0.74 & 0.66\\
Au-19 & 0.95 & 0.67 & 0.91 & 0.63 & 0.89 & 0.63 & 0.83 & 0.64 & 0.85 & 0.69\\
Au-20 & 0.81 & 0.58 & 0.91 & 0.64 & 0.95 & 0.71 & 0.97 & 0.78 & 0.86 & 0.77\\
Au-21 & 0.98 & 0.74 & 0.97 & 0.82 & 0.97 & 0.87 & 0.99 & 0.88 & 0.99 & 0.99\\
Au-22 & 0.96 & 0.84 & 0.93 & 0.84 & 0.93 & 0.85 & 0.95 & 0.87 & 0.97 & 0.88\\
Au-23 & 0.94 & 0.65 & 0.96 & 0.64 & 0.94 & 0.65 & 0.92 & 0.69 & 0.93 & 0.74\\
Au-24 & 0.99 & 0.67 & 1.00 & 0.63 & 0.99 & 0.65 & 0.97 & 0.68 & 0.98 & 0.70\\
Au-25 & 0.97 & 0.71 & 0.96 & 0.73 & 0.86 & 0.74 & 0.67 & 0.64 & 0.71 & 0.67\\
Au-26 & 0.96 & 0.76 & 0.97 & 0.73 & 0.97 & 0.70 & 0.99 & 0.68 & 0.97 & 0.67\\
Au-27 & 0.98 & 0.73 & 0.97 & 0.75 & 0.97 & 0.79 & 0.96 & 0.79 & 0.95 & 0.77\\
Au-28 & 0.98 & 0.82 & 0.94 & 0.77 & 0.88 & 0.73 & 0.86 & 0.74 & 0.93 & 0.75\\
Au-29 & 0.91 & 0.81 & 0.89 & 0.72 & 0.87 & 0.69 & 0.84 & 0.68 & 0.85 & 0.69\\
Au-30 & 0.89 & 0.73 & 0.78 & 0.64 & 0.69 & 0.53 & 0.80 & 0.58 & 0.91 & 0.63\\
  \hline\hline
  \end{tabular}
  \label{tab}
  \caption{Magnetic field properties of the Auriga galaxies at $z=0$. For general properties of the disks.}
\end{table*}
